% !TeX spellcheck = en_GB
% !TeX encoding = UTF-8

\section*{Abstract}
\label{sec:abstract}

Deep learning models boast remarkable predictive capabilities, and they will work on image recognition tasks within upload filters. But what else can these models tell about their decisions? If these models are used in practice, they shall not only be work excellent but be transparent. And yet the task of making models transparent appears underspecified if it comes to the usage of these models in upload filters. Papers provide diverse solutions for transparent models and offer myriad notions of what attributes render models transparent. In this paper, I seek to refine the discourse on transparent models for image recognition. First, the motivation and underlying interest in transparent models get examined, finding them to be diverse. Then, model properties and techniques thought to confer transparency gets addressed, identifying SHAP values as a suitable method of doing so. Based on a prototype, the feasibility of an explainable model within an upload filter gets discussed. Furthermore, the assertion that explainable artificial intelligence can improve the user experience of upload filters within social media gets questioned. 

\section*{Preface}
Machine Learning has grown large in both research and industrial applications, especially with the success of deep learning and so-called neural networks, so extensive that its impact and possible after-effects are unpredictable. Interpretability, explainability and transparency of machine learning algorithms have thus become pressing issues. For this reason, I started to gain intrinsic motivation about machine learning, deep learning and explainable artificial intelligence. 

I first came into contact with Data Science through an IT project.  I modified a remote-controlled car so that it was possible to control it with a Raspberry Pi. The final step was to implement a neural network for autonomously driving. The whole project was very challenging. But I had a lot of fun, and my passion was awakened. My knowledge and motivation were immediately tested in Hong Kong, while I focused on machine learning during my semester abroad. The mathematical theorems that were expected to be solved were genuine hurdle because of my gaps in mathematics. Tanks to the enormous effort, however, I achieved huge breakthroughs, was able to close the gaps, master the tasks and finally shine at the practical programming part.

This experience strengthened my wish to specialize further in this direction. Throughout this thesis, I will question the oft-made assertions that linear models are transparent and that deep neural networks are not. I think this is important since there is a lot of ambiguity when it comes to the use of deep learning methods within upload filters. 