% !TeX spellcheck = en_GB
% !TeX encoding = UTF-8

\chapter{Conclusion}
\epigraph{"It is beyond a doubt that all our knowledge begins with experience."}{- Immanuel Kant}
\label{ch:conclusion}


I think the rise of deep learning has been defined by a shift away from transparent and understandable human-written code towards complicated black boxes. Their creators have still little understanding of how or even why the algorithms came to a specific decision. The use of these complicated models in real-world situations like upload filters leads to a need for transparent models. 

\section{Metaphoric interpretation of the evaluation and the generalization}

I think it can be compared with the development of programming languages. In the beginning, these were difficult for people to understand. It took experts to use them for programming applications. Even today an excellent training is vital to use these tools professionally. But the handling has become more accessible and more intuitive for humans. Today it is possible that even kids can have fun with simple programming tasks and learn to use them intuitively. In this metaphor, the beginning of the programming languages stands for the theory chapter. It can be seen how complicated the connection between the recognition of patterns on images and the associated decision making is. In the following, the prototype showed how a simple visualization could lead to an improved intuition of a deep learning model. I believe that as shown in the generalization chapter, a lot of work in different areas is necessary to get to the same level as simplicity as in some "toy" programming languages like Scratch today. 

I hope that this development will take place and that in a few years it will be possible for everyone to use these programs intuitively. Even if it still needs some experience in this field, it should be possible for everyone who is affected by an algorithmic decision to understand that decision. Th upload filters are an example of why this is important. Also, the corresponding discussion in the media and protests around the upload filter discussion shows that at least in Germany, there is an interest in the understanding of how algorithms make decisions. 


\section{Personal Statement}

I hope to be able to meet this interest and responsibility in my master's degree, which computer scientists have when it comes to making deep learning models more transparent. 
